### 2024-01-29 tesis_Ashish/Chapter5/chapter5.tex
29 Jan update

%Background subtraction and beam corrections have been applied to the raw data to account for noise.
%Chi2/ndof for all vdM and Imaging Scans:
%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit. A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit. PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb as shown in Fig. \ref{fig:period_bound_105} \cite{pas_22} %\cite{bril2023vdmrecalibration}.

@@

\newpage
\subsection{Afterglow background corrections}

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
\caption[2022 PCC Type 1 Afterglow Residuals]{%                                                                                                                                                                             
 PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F. The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
\caption[2022 PCC Type 2 Afterglow Residuals]{%
  Type 2 residual as a function of instantaneous luminosity for period 2022F. These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
}
\label{fig:period_bound_45}
\end{figure}

@@

\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Fig. \ref{fig:period_bound_99}. Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing. %These variations are important to monitor as they can impact the precision of the luminosity measurement, which in turn affects the accuracy of the results obtained from the physics analyses conducted with the data.
If significant variations are observed, it may be necessary to adjust the analysis to account for these differences.

>>>>

%Background subtraction and beam corrections have been applied to the raw data to account for noise.
%Chi2/ndof for all vdM and Imaging Scans:
%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit. A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit. PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb. The bunch to bunch variation and scan to scan variation of PCC visible cross section is shown in Fig. \ref{fig:period_bound_99} and Fig. \ref{fig:period_bound_105} \cite{pas_22} %\cite{bril2023vdmrecalibration}.

@@

%\newpage
\subsection{Afterglow background corrections}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
\caption[2022 PCC Type 1 Afterglow Residuals]{%                                                                                                                                                                             
 PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F. The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
\caption[2022 PCC Type 2 Afterglow Residuals]{%
  Type 2 residual as a function of instantaneous luminosity for period 2022F. These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
}
\label{fig:period_bound_45}
\end{figure}

@@

\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another. Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing. %These variations are important to monitor as they can impact the precision of the luminosity measurement, which in turn affects the accuracy of the results obtained from the physics analyses conducted with the data.
If significant variations are observed, it may be necessary to adjust the analysis to account for these differences.

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_btob_variation.png}
%\caption[$\sigma_{vis}$ Bunch Variation]{%                                                                                                                                             
 % Bunch to bunch variation of PCC visible cross section where the red line is the average value. Red band depicts the $\pm$ one RMS of the values.
%}
%\label{fig:period_bound_99}
%\end{figure}
